### 2016-07-04 Renormalization.tex
uncertainties for squark production in table

In the case of the MRSSM it will turn out that the only supersymmetry violation comes from corrections associated with the gluon, as already alluded to in section \ref{sec:RegSchemes}. However, supersymmetry restoring will always already be included in $\delta Z^{\mathrm{DREG}}$. Referring to the field renormalization constants from eq. \ref{eq:fieldtrafo}, this is 

@@

is the supersymmetry restoring renormalization constant. Note the sign within this definition in comparison to eq. \ref{eq:GammaCtRestore}. The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms, due to different loop diagrams. Therefore one has to make a difference between these couplings at 1-loop level. In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in subsection \ref{sec:RenGaugeCoupling}). The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.

@@

\subsection{On-Shell Renormalization}\label{sec:QuarkSE}
A part of the computation of the cross section at next-to-leading order is the calculation of renormalization constants. 
Field renormalization constants $\delta Z$ and parameter renormalization constants $\delta o$ with $o \in \left\{ g, m \right\}$ are defined by
\begin{align}
Z = 1 + \delta Z \hspace{3cm} o_{\mathrm{bare}} = o + \delta o
\end{align}
where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq. \ref{eq:fieldtrafo} and \ref{eq:fieldtrafo}. The field and mass renormalization constants have been calculated in DREG in the on-shell scheme. This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.\\
The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk}.

\subsubsection*{The Quark Self-Energy}
The quark self-energy splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level.}\label{fig:QuarkSelfEnergy}
\end{center}
\end{figure}\\
The one-particle-irreducible diagrams evaluate to
\begin{align}
i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
\end{align}
With the counterterm Feynman rule\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[fermionbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionbar] (0,0) --(1.3,0);
	\node at (1.6,-0.1) {$j$};
	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
\end{scope}
\end{tikzpicture}\\
and the on-shell renormalization condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0
\end{align}
where $\Re (\hdots)$ denotes the real part of $\hdots$ one finds
\begin{align}
\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right].
\end{align}
Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$. These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} defined to be zero. Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part. Note further that the term $\frac{1}{2}$ from eq. \ref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
\begin{align}
\delta Z_q^{\mathrm{trans}} = \delta Z_q^{\mathrm{DREG}} - \delta Z_q^{\mathrm{DRED}} = C(F) \frac{g_s^2}{16\pi^2}.\label{eq:QuarkSC}
\end{align}

@@

The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the "actual" gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and may be referred to as the octino.\\
From the Lagrangian \ref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct. This is reflected by different field renormalization constants of the left- and right-handed part of the gluino.

@@

Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks the renormalization constant for the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added. This is also true in a more general case, i.e. the renormalization constants of virtual particles do always drop out.

@@

The term in the curved brackets of eq. \ref{eq:qqGlight} corresponds to the first diagram in fig. \ref{fig:GaugeCouplingCorrection} whereas the term with the prefactor $C(A)$ corresponds to the second diagram. 

@@

\subsection{The Beta Function}\label{sec:beta_function}
The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
Writing down the action of a theory in $D$ dimensions, one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless. But $\mu$ is no physical parameter but can be absorped into the fields and parameters. To this end one defines
\begin{align}
g_{sB}(g_s, \mu) = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
\end{align}
which must not depend upon the unphysical scale $\mu$, ergo
\begin{align}
0 = \frac{\mathrm{d}g_{sB}}{\mathrm{d}\ln\mu} = \frac{\partial g_{sB}}{\partial \ln\mu} + \beta \frac{\partial g_{sB}}{\partial g_s}\label{eq:beta_func}
\end{align}
where the definition of the beta function $\frac{\partial g_s}{\partial\ln\mu}$ has been inserted. Equation \ref{eq:beta_func} serves to calculate $\beta(g_s,\epsilon)$.  By equating coefficients and using the shortcuts
\begin{align*}
\frac{\beta_0^L}{2} &= \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A)\\
\frac{\beta_0^H}{2} &= \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f\\
L &= - \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)
\end{align*}
so that 
\begin{align}
\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{\beta^L_0}{2\epsilon_{\mathrm{UV}}} + \frac{\beta^H_0}{2\epsilon_{\mathrm{UV}}} + L \right)
\end{align}
one finds
\begin{align}
\beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mathrm{2-loop})\\
\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L + \mathcal{O}(\mathrm{2-loop}).
\end{align}
This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx} Gross and Wilczek \cite{Gross:1973ju}. This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.

\subsection{Supersymmetry Restoring Counterterm}\label{sec:SUSYrestore}
As already discussed in section \ref{sec:RegSchemeDep} care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$. In doing so one needs the already calculated transition counterterms of the quark, squark and gluino from eq. \ref{eq:QuarkSC}, \ref{eq:SquarkSC} and \ref{eq:GluinoSC}
as well as the transition counterterm of the gluon.
\subsubsection*{The Gluon Self-Energy Revisited}
The only regularization dependence of the gluon self-energy arises from the gluon loop, i.e. the last diagram in figure \ref{fig:lightGluonSelfEnergy}. With the definition of $\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}}$ in eq. \ref{eq:GammaCtRestore} one obtains
\begin{align}
i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG},G_\mu^a G_\nu^b} = -i\frac{1}{3} C(A) \frac{g_s^2}{16\pi^2}(p^2 g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
\end{align}
which translates to the transition counterterm
\begin{align}
\delta Z^{\mathrm{trans}}_G = \frac{C(A)}{3}\frac{g_s^2}{16\pi^2}.
\end{align}

@@

\subsubsection*{The $q\tilde{q}^\dagger\tilde{g}$ Vertex Correction}
The supersymmetry restoring corrections to the Yukawa coupling originate from the diagram below.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow](180:1.3)--(180:0.5);
	\draw[gluon](180:0.5)--(45:0.5);
	\node at (0,0.5) {$G$};
	\draw[fermionnoarrow](180:0.5)--(-45:0.5);
	\draw[gluon](180:0.5)--(-45:0.5);
	\node at (0,-0.5) {$\tilde{g}$};
	\draw[fermion](45:0.5)--(-45:0.5);
	\node at (0.7,0) {$q$};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[scalarbar](-45:0.5)--(-45:1.3);
\end{tikzpicture}
\caption{Diagram of the supersymmetry restoring correction of  the $q\tilde{q}\tilde{g}$ vertex}
\end{center}
\end{figure}
The supersymmetry restoring part is given by
\begin{align}
i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}, q_i\tilde{q}_j\tilde{g}^a} &= -ig_s \sqrt{2} P_L T^a_{ij}  \frac{g_s^2}{16\pi^2}C(A)\\
&= -ig_s \sqrt{2} P_L T^a_{ij}  \left[ \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} + \frac{\delta Z^{\mathrm{trans}}_q + \delta Z^{\mathrm{trans}}_{\tilde{q}} + \delta Z^{\mathrm{trans}}_{\tilde{g}}}{2} \right].
\end{align}
The supersymmetry restoring part of the Yukawa renormalization constants is therefore
\begin{align}
\frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} = -\frac{C(F)-C(A)}{2} \frac{g_s^2}{16\pi^2}.
\end{align}
As a consequence of the two different supersymmetry restoring parts of the coupling renormalization constants an additional renormalization constant $\delta g_s^{\mathrm{restore}}$ needs to be introduced. As described in section \ref{sec:RegSchemeDep} it is given by
\begin{align}
\frac{\delta g_s^{\mathrm{restore}}}{g_s} = \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} -\frac{\delta g_s^{\mathrm{trans}}}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{2C(A)}{3} - \frac{C(F)}{2} \right).
\end{align}
In short this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in \ref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormilzed with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
The finite correction $\delta g_s^{\mathrm{restore}}$ is the same as in supersymmetric QCD which should not surprise too much as all its contributions originate from loops with gluons.% So there are no new contributions in RSQCD with respect to SQCD.

>>>>

In the case of the MRSSM it will turn out that the only supersymmetry violation comes from corrections associated with the gluon, as already alluded to in section \ref{sec:RegSchemes}. However, supersymmetry restoring will always already be included in $\delta Z^{\mathrm{DREG}}$. Referring to the field renormalization constants from eq. \eqref{eq:fieldtrafo}, this is 

@@

is the supersymmetry restoring renormalization constant. Note the sign within this definition in comparison to eq. \eqref{eq:GammaCtRestore}. The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms, due to different loop diagrams. Therefore one has to make a difference between these couplings at 1-loop level. In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in subsection \ref{sec:RenGaugeCoupling}). The Yukawa coupling $\hat{g}_s$ therefore needs to be added with the difference of the supersymmetry restoring counterterms from the $q\tilde{q}^\dagger\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.

@@

\subsection{On-Shell Renormalization}\label{sec:QuarkSE}
A part of the computation of the cross section at next-to-leading order is the calculation of renormalization constants. 
Field renormalization constants $\delta Z$ and parameter renormalization constants $\delta o$ with $o \in \left\{ g, m \right\}$ are defined by
\begin{align}
Z = 1 + \delta Z \hspace{3cm} o_{\mathrm{bare}} = o + \delta o
\end{align}
where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq. \eqref{eq:fieldtrafo} and \eqref{eq:fieldtrafo}. The field and mass renormalization constants have been calculated in DREG in the on-shell scheme. This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.\\
The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
The renormalization constants are given in terms of Passarino-Veltman integrals whose definition may be found in Appendix \ref{sec:Passarino}.

\subsubsection*{The Quark Self-Energy}
The quark self-energy splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level.}\label{fig:QuarkSelfEnergy}
\end{center}
\end{figure}\\
The one-particle-irreducible diagrams evaluate to
\begin{align}
i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
\end{align}
With the counterterm Feynman rule\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[fermionbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionbar] (0,0) --(1.3,0);
	\node at (1.6,-0.1) {$j$};
	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
\end{scope}
\end{tikzpicture}\\
and the on-shell renormalization condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0
\end{align}
where $\Re (\hdots)$ denotes the real part of $\hdots$ one finds
\begin{align}
\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right].
\end{align}
Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$. These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} defined to be zero. Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part. Note further that the term $\frac{1}{2}$ from eq. \eqref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
\begin{align}
\delta Z_q^{\mathrm{trans}} = \delta Z_q^{\mathrm{DREG}} - \delta Z_q^{\mathrm{DRED}} = C(F) \frac{g_s^2}{16\pi^2}.\label{eq:QuarkSC}
\end{align}

@@

The left-handed part $\lambda^a$ is associated with the superpartner of the gluon and therefore the ``actual'' gluino whereas the right-handed part $\overline{\chi}^a$ was introduced to assign a Dirac-mass to the gluino and may be referred to as the octino.\\
From the Lagrangian \eqref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct. This is reflected by different field renormalization constants of the left- and right-handed part of the gluino.

@@

Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks, the renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added. This is also true in a more general case, i.e. the renormalization constants of virtual particles do always drop out.

@@

The term in the curved brackets of eq. \eqref{eq:qqGlight} corresponds to the first diagram in fig. \ref{fig:GaugeCouplingCorrection} whereas the term with the prefactor $C(A)$ corresponds to the second diagram. 

@@

\subsection{The Beta Function}\label{sec:beta_function}
The beta function describes the dependence of the gauge coupling $g_s$ upon the energy scale $\mu$.\\
Writing down the action of a theory in $D$ dimensions, one needs to introduce an energy scale $\mu$ in order to keep the action dimensionless. But $\mu$ is no physical parameter but can be absorped into the fields and parameters. To this end one defines
\begin{align}
g_{sB}(g_s, \mu) = \mu^\epsilon g_s \left( 1 + \frac{\delta g_s}{g_s} \right)
\end{align}
which must not depend upon the unphysical scale $\mu$, ergo
\begin{align}
0 = \frac{\mathrm{d}g_{sB}}{\mathrm{d}\ln\mu} = \frac{\partial g_{sB}}{\partial \ln\mu} + \beta \frac{\partial g_{sB}}{\partial g_s}\label{eq:beta_func}
\end{align}
where the definition of the beta function $\frac{\partial g_s}{\partial\ln\mu}$ has been inserted. Equation \eqref{eq:beta_func} serves to calculate $\beta(g_s,\epsilon)$.  By equating coefficients and using the shortcuts
\begin{align*}
\frac{\beta_0^L}{2} &= \frac{2}{3}T(F)(n_f-1) - \frac{11}{6}C(A)\\
\frac{\beta_0^H}{2} &= \frac{5}{6}C(A) + \frac{2}{3}T(F) + \frac{1}{3}T(F)n_f\\
L &= - \frac{2}{3} C(A) \ln \frac{m_{\tilde{g}}^2}{\mu^2} - \frac{1}{3}T(F)n_f \ln \frac{m_{\tilde{q}}^2}{\mu^2} - \frac{2}{3}T(F) \ln \frac{m_t^2}{\mu^2}-\frac{1}{12} C(A) \left( \ln \frac{m_{\phi^0}^2}{\mu^2} + \ln \frac{m_{\sigma^0}^2}{\mu^2} \right)
\end{align*}
so that 
\begin{align}
\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{\beta^L_0}{2\epsilon_{\mathrm{UV}}} + \frac{\beta^H_0}{2\epsilon_{\mathrm{UV}}} + L \right)
\end{align}
one finds
\begin{align}
\beta(g_s,\epsilon) &= -\epsilon g_s \left( 1 + \frac{g_s^2}{16\pi^2} L \right) + \beta(g_s) + \mathcal{O}(\mathrm{2-loop})\\
\beta(g_s) &= \frac{g_s^3}{16\pi^2} \beta_0^L + \mathcal{O}(\mathrm{2-loop}).
\end{align}
This is the beta function of QCD first found by Politzer \cite{Politzer:1973fx} Gross and Wilczek \cite{Gross:1973ju}. This means that renormalizing $g_s$ in the way it is, decouples heavy particles from the $\beta$ function and allows to adopt $\alpha_s = \frac{g_s^2}{4\pi}$ from the parton density functions.

\subsection{Supersymmetry Restoring Counterterm}\label{sec:SUSYrestore}
As already discussed in section \ref{sec:RegSchemeDep} care is required in terms of supersymmetry restoring when renormalizing  the gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$. In doing so one needs the already calculated transition counterterms of the quark, squark and gluino from eq. \eqref{eq:QuarkSC}, \eqref{eq:SquarkSC} and \eqref{eq:GluinoSC}
as well as the transition counterterm of the gluon.
\subsubsection*{The Gluon Self-Energy Revisited}
The only regularization dependence of the gluon self-energy arises from the gluon loop, i.e. the last diagram in figure \ref{fig:lightGluonSelfEnergy}. With the definition of $\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}}$ in eq. \eqref{eq:GammaCtRestore} one obtains
\begin{align}
i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG},G_\mu^a G_\nu^b} = -i\frac{1}{3} C(A) \frac{g_s^2}{16\pi^2}(p^2 g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}
\end{align}
which translates to the transition counterterm
\begin{align}
\delta Z^{\mathrm{trans}}_G = \frac{C(A)}{3}\frac{g_s^2}{16\pi^2}.
\end{align}

@@

\subsubsection*{The $q\tilde{q}^\dagger\tilde{g}$ Vertex Correction}
The supersymmetry restoring corrections to the Yukawa coupling originate from the diagram below.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow](180:1.3)--(180:0.5);
	\draw[gluon](180:0.5)--(45:0.5);
	\node at (0,0.5) {$G$};
	\draw[fermionnoarrow](180:0.5)--(-45:0.5);
	\draw[gluon](180:0.5)--(-45:0.5);
	\node at (0,-0.5) {$\tilde{g}$};
	\draw[fermion](45:0.5)--(-45:0.5);
	\node at (0.7,0) {$q$};
	\draw[fermionbar](45:0.5)--(45:1.3);
	\draw[scalarbar](-45:0.5)--(-45:1.3);
\end{tikzpicture}
\caption{Diagram of the supersymmetry restoring correction of  the $q\tilde{q}\tilde{g}$ vertex}
\end{center}
\end{figure}
The supersymmetry restoring part is given by
\begin{align}
i\Gamma^{\mathrm{(1),ct,trans}}_{\mathrm{DREG}, q_i\tilde{q}_j\tilde{g}^a} &= -ig_s \sqrt{2} P_L T^a_{ij}  \frac{g_s^2}{16\pi^2}C(A)\\
&= -ig_s \sqrt{2} P_L T^a_{ij}  \left[ \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} + \frac{\delta Z^{\mathrm{trans}}_q + \delta Z^{\mathrm{trans}}_{\tilde{q}} + \delta Z^{\mathrm{trans}}_{\tilde{g}}}{2} \right].
\end{align}
The supersymmetry restoring part of the Yukawa renormalization constants is therefore
\begin{align}
\frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} = -\frac{C(F)-C(A)}{2} \frac{g_s^2}{16\pi^2}.
\end{align}
As a consequence of the two different supersymmetry restoring parts of the coupling renormalization constants an additional renormalization constant $\delta g_s^{\mathrm{restore}}$ needs to be introduced. As described in section \ref{sec:RegSchemeDep} it is given by
\begin{align}
\frac{\delta g_s^{\mathrm{restore}}}{g_s} = \frac{\delta \hat{g}_s^{\mathrm{trans}}}{g_s} -\frac{\delta g_s^{\mathrm{trans}}}{g_s} = \frac{g_s^2}{16\pi^2}\left( \frac{2C(A)}{3} - \frac{C(F)}{2} \right).
\end{align}
In short this means that the gauge coupling $g_s$ is renormalized with $\delta g_s$ given in \eqref{eq:deltaGs} and the Yukawa coupling $\hat{g}_s$ is renormilzed with $\delta \hat{g}_s = \delta g_s + \delta g_s^{\mathrm{restore}}$.\\
The finite correction $\delta g_s^{\mathrm{restore}}$ is the same as in supersymmetric QCD which should not surprise too much as all its contributions originate from loops with gluons.% So there are no new contributions in RSQCD with respect to SQCD.

\subsection{$\overline{\mathrm{MS}}$ - Renormalization}\label{sec:MSRen}
To quickly check for UV-finiteness of a Greenfunction or a physical observable it is useful to have the extracted UV-divergences of the renormalization constants at hand. How these are obtained is described in \ref{sec:Passarino}.
\begin{align}
& \delta Z_{\tilde{g}}^L = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2\left[ T(F) n_f + C(A) \right] &&  \delta Z_{\tilde{g}}^R = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2 C(A)\nonumber\\
& \delta m_{\tilde{g}} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} \left[ T(F) n_f - 2C(A) \right] m_{\tilde{g}}\nonumber\\
& \delta Z_{\tilde{q}} = 0 && \delta m_{\tilde{q}}^2 = 0\nonumber\\
&\frac{\delta g_s}{g_s} = \frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ T(F) n_f - C(A) \right] = 0\nonumber\\
& \delta Z_{\phi^0} = 0 && \delta m_{\phi^0}^2 = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}}\left[ 8T(F)n_f - 16C(A) \right]m_{\tilde{g}}^2\nonumber\\
& \delta Z_{\sigma^0} = 0 && \delta m_{\sigma^0}^2 = 0\nonumber\\
& \delta Z_{G} = -\frac{g_s^2}{16\pi^2\epsilon_{\mathrm{UV}}} 2T(F) n_f
\end{align}
Note that the renormalization constants $\delta m_{\tilde{g}}$, $\delta m^2_{\phi^0}$ and $\delta m^2_{\sigma^0}$ are not independent from each other as the masses of the gluino and the two sgluons stam from only two parameters, i.e. $m_{\tilde{g}}$ and $m_{\sigma}^2$ from the softly breaking part of the Lagrangian, eq. \eqref{eq:L_RSQCD}. 
In additions it happens that the particle content of RSQCD is such that $\frac{\delta g_s}{g_s} = 0$. This means that the $\beta$ function of $g_s$ equals zero at 1-loop-level if one does not choose to decouple heavy particles from the running as has been done in this thesis. However at 2-loop-level there is a non-zero $\beta$ function of $g_s$, which has been calculated by \texttt{SARAH}.
